Cover Your Basis: Comprehensive Data-Driven Characterization of the Binary Black Hole Population

### 2022-10-11 src/tex/ms.tex
update title
update title and abstract

\title{Cover Your Basis: Comprehensive Model Agnostic Probes of the Binary Black Hole Population}

@@

\begin{abstract}                 
We introduce a non-parametric model built from basis splines and use it to infer the astrophysical distribution of 
binary black hole (BBH) masses and spins using the 69 confident observations in GWTC-3, which marks this work as 
the most comprehensive data-driven investigation of the BBH population to date. We report the same features previously recovered 
with similarly flexible models focusing solely on the mass distribution, most notably the peaks in merger rates at $\sim10\msun$ and $\sim35\msun$. 
Our study provides the first non-parametric investigation into BBH spin distribution, while simultaneously modeling the mass distribution in the same way, 
showing signs that the spin tilt distributions may not peak at $\cos(\theta_i) = 1$ as previous models assumed. We find broad agreement with the 
accepted conclusions of the spin magnitude distribution: the majority of BBH spins are small ($a<0.5$), the distribution peaks at $a\sim0.2$, 
and there is mild support for a non-spinning subpopulation, which may become resolvable with larger catalogs. 
We perform a data-driven test to determine if the data prefers differing spin distributions for each binary component, and 
find no strong sign that the distributions differ. We conclude with a discussion of how non-parametric methods in 
gravitational-wave population inference are uniquely poised to complement to the parametric approach as we enter the 
data-rich era of gravitational-wave astronomy.

>>>>

\title{Cover Your Basis: Comprehensive Data-Driven Characterization of the Binary Black Hole Population}

@@

\begin{abstract}                 
We introduce the first complete non-parametric models for the astrophysical distribution of the binary black hole (BBH) population.  Using the 69 confident observations in GWTC-3, we present the most comprehensive data-driven investigation of the BBH population to date, including BBH mass ratio, spin magnitudes and misalignments, and redshift. We report the same features previously recovered 
with similarly flexible models of the mass distribution, most notably the peaks in merger rates at primary masses of ${\sim}10\msun$ and ${\sim}35\msun$.  We infer a distribution for primary spin misalignments that peaks away from alignment, supporting recent work that used a variety of parameterized models to come to the same conclusion. We find broad agreement with the 
previous inferences of the spin magnitude distribution: the majority of BBH spins are small ($a<0.5$), the distribution peaks at $a\sim0.2$, 
and there is mild support for a non-spinning subpopulation, which may be resolved with larger catalogs. 
Using our non-parametric models, we explore whether the data support spin distributions unique for each binary component, and 
find no strong evidence that the distributions differ. We conclude with a discussion of how non-parametric methods in 
gravitational-wave population inference are uniquely poised to complement to the parametric approach as we enter the 
data-rich era of gravitational-wave astronomy.
